\LARGE \bf A Semi-Automated Software Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-04-16 paper.tex
remove commented out sections because we can always revert with git
fixed histograms to not count duplicate videos

% REMOVED IN REVISION
% Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.

% \begin{figure}[htbp]
%     \centering
%     \tikzset{
%         node distance = 6mm and 0cm,
%         module/.style={%
%             draw, rounded corners,
%             minimum width=#1,
%             minimum height=7mm,
%             font=\sffamily
%             },
%         module/.default=1cm,
%         >=LaTeX
%     }
%     \begin{tikzpicture}[
%       % This will show the frame around the figure
%       show background rectangle]

%       % Place first 6 items
%       \node[module] (crawler) {Web-Scrapers};
%       \node[module, below=of crawler] (downloader) {Downloaders};
%       \node[module, below=of downloader] (splitter) {Video-Splitter};
%       \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
%       \node[module, below=of labeller] (uploader) {Data-Uploader};
%       \draw[->] (crawler) -- (downloader);
%       \draw[->] (downloader) -- (splitter);
%       \draw[->] (splitter) -- (labeller);
%       \draw[->] (labeller) -- (uploader);

%     \end{tikzpicture}
%         \caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
%         \label{fig:pipeline-architecture}
% \end{figure}

% Users may define their own search terms to be used when querying the video repository. This value can be set in a YAML pipeline configuration file. By default, our scrapers query using the keywords: \texttt{Car crash dashcam}. Currently we support crawling Reddit and YouTube to locate videos that are of interest, and downloading videos hosted on YouTube and Imgur. Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface. This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader. \texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations. The \texttt{UniversalDownloader} then distributes \texttt{MetaDataItem} objects to their corresponding downloader by matching source URLs through regular expressions. New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.

%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we anonymize personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video. The executor then applies a blurring mask over each bounding box and writes the modified frame back to the video stream. We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.

@@

\subsection{Annotation}

% In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos. Following Chan et al.\cite{chan2016anticipating}, if a collision occurs, we provide tools to annotate the frame where the collision occurs and bounding boxes to localize, identify and track agents in the video segment. Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling. We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit variable download resolutions. 
% Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.

% \subsection{Metadata}
% After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
% There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):

% \begin{itemize}
%   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
%   \item "\texttt{description}": Description of the video as scraped from the video hosting website
%   \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
%   \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
%   \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
%   \item "\texttt{title}": The title of the video from the video hosting website
%   \item "\texttt{url}": URL that the video was fetched from
%   \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
%   \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
%   \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
%   \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
%   \item "\texttt{bb\_fields}": All bounding-box specific data
%   \begin{itemize}
%     \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
%     \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
%     \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
%     \begin{itemize}
%       \item "\texttt{id}": Unique numerical identifier that represents this object
%       \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a $1\times5$ array with elements in the following order: frame number, x1, y1, x2, y2
%       \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
%       \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
%     \end{itemize}
%   \end{itemize}
% \end{itemize}

% \begin{figure}[htbp]
%   \begin{lstlisting}[language=json,xleftmargin=5mm]
% {
%   "description":"",
%   "download_src":"YouTube",
%   "tags": {
%     "reddit_post_info":{
%       "id":"<post_id>"
%       "title":"title"
%     }
%   },
%   "title":"Title of the Video",
%   "url":"http://www.myvideo.com",
%   "is_split_url": false,
%   "enum_tags": ["NoCollision"],
%   "start_i": 0,
%   "end_i": 60,
%   "bb_fields": {
%     "collision_locations": [],
%     "objects": [
%       {
%         "bboxes": [
%           [0, 1096, 377, 1279, 634]
%         ],
%         "class": "car",
%         "has_collision": false,
%         "id": "1"
%       }
%     ],
%     "resolution": [1280, 720]
%   }
% }
%   \end{lstlisting}
%     \caption{Example metadata produced by the pipeline}
%     \label{metadata_example}
% \end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Objects by class},
    ylabel={Frequency (\# of objects)},
    ymin=-50,
    ymax=1800,
    xtick=data,
    xticklabels from table={\byclass}{X},
    xticklabel style={rotate=50,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by object class}
    \label{fig:obj-by-class}
\end{figure}

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Videos by participant},
    xlabel={Number of participants},
    ylabel={Frequency (\# of videos)},
    ymin=-5,
    ymax=175,
    xtick=data,
    xticklabels from table={\byactors}{X},
    xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by number of participants}
    \label{fig:vids-by-participant}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Videos by agents},
    xlabel={Number of agents},
    ylabel={Frequency (\# of videos)},
    ymin=-10,
    ymax=270,
    xtick=data,
    xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by number of agents}
    \label{fig:vids-by-agents}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Videos by duration},
    xlabel={Duration (in frames)},
    ylabel={Frequency (\# of videos)},
    xtick=data,
    ymin=-5,
    ymax=130,
    xticklabels from table={\byduration}{X},
    xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by duration}
    \label{fig:vids-by-duration}
\end{figure}

>>>>

\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we anonymize personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video. The executor then applies a blurring mask over each bounding box and writes the modified frame back to the video stream. We have chosen to use a MobileNet SSD for this task because it achieves a good balance between accuracy and performance, while requiring relatively little memory \cite{yixuan_h_y_hu_2021_4642275}.

@@

@@

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Objects by class},
    ylabel={Frequency (\# of objects)},
    ymin=-25,
    ymax=800,
    xtick=data,
    xticklabels from table={\byclass}{X},
    xticklabel style={rotate=50,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by object class}
    \label{fig:obj-by-class}
\end{figure}

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Videos by participant},
    xlabel={Number of participants},
    ylabel={Frequency (\# of videos)},
    ymin=-5,
    ymax=130,
    xtick=data,
    xticklabels from table={\byactors}{X},
    xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by number of participants}
    \label{fig:vids-by-participant}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Videos by agents},
    xlabel={Number of agents},
    ylabel={Frequency (\# of videos)},
    ymin=-5,
    ymax=112,
    xtick=data,
    xticklabels from table={\byagents}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byagents;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by number of agents}
    \label{fig:vids-by-agents}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \begin{tikzpicture}
    \begin{axis}[
    title={Videos by duration},
    xlabel={Duration (in frames)},
    ylabel={Frequency (\# of videos)},
    xtick=data,
    ymin=-2,
    ymax=70,
    xticklabels from table={\byduration}{X},
    xticklabel style = {rotate=45,anchor=east,yshift=-2mm}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
    \caption{Distribution of videos in pre-processed prototype dataset by duration}
    \label{fig:vids-by-duration}
\end{figure}
